---
title: "Lab7"
author: "Tiana Chen"
date: "2024-10-17"
output: "github_document"
---
# Load packages and dataset
```{r}
library(haven)
library(bruceR)
library(dplyr)
library(ggstatsplot)
library(performance)
library(sjPlot)

ex <- read_sav("/Users/chenxuejing/Documents/GitHub/Lab7/ex.sav")

lab7<-read.csv("/Users/chenxuejing/Documents/GitHub/Lab7/lab7.csv")



```

# Correlation
```{r}
#First, you will need to select variables or composites of interest

ex <- ex %>%
  select(Conscientiousness, AverageHoursofSleep, GPA)

#The Corr function also gives you a correlation plot between all variables, but it doesn't look pretty enough and not very customisable 

Corr(ex)

#If you hate the correlation plot design, you can use the following function
ggcorrmat(ex)

#If you want to visualize the correlation between two specifcic variables, you can use the following code
ggplot(ex, aes(x = Conscientiousness, y = GPA)) + geom_point() + geom_smooth() + theme_bruce()

#Note that the line will naturally follow the data points, but you can specify to plot the fittest line by adding method = lm to the geom_smooth() function
ggplot(ex, aes(x = Conscientiousness, y = GPA)) + geom_point() + geom_smooth(method = lm) + theme_bruce()




```

# Regression
```{r}
#step 1: build a model lm=linear model, and GPA~Conscientiousness means that 'gpa predicted by conscientiousness'
model<-lm(GPA ~ Conscientiousness + AverageHoursofSleep, data = ex)


#step 2: check the assumptions
check_model(model)

#step 3: summarize results; add ,std = TRUE if you want to get standardized coefficients
model_summary(model)


# or using the tab_model functional; add  ,show.std = TRUE if you want to get standardized coefficients
tab_model(model)

#step 4: plot the results; change type ="est" to type = "std" if you want to plot the standardized coefficients
plot_model(model,  type ="est",  show.values = TRUE, vline.color = "#1B191999", line.size = 1.5, dot.size = 2.5, colors = "blue") + theme_bruce()



```




# Q1: Use the Corr or the ggcorrmat function to plot the correlation between all variables. Which personality traits are correlated with satisfaction with life and which one is not? 
```{r}

Corr(lab7)
# Openness is not significantly correlated with satisfaction with life, while Extraversion, Agreeableness, Conscientiousness, and Emotional Stability are.
```

# Q2: Run a multiple regression using the Big 5 personality traits to predict satisfaction with life and plot the results
```{r}
#for this lab assignment you would assume assumptions are met, but for your own analysis, you will need to examine assumptions carefully
model_lab7<-lm(SWL ~ Extraversion + Agreeableness + Conscientiousness + EmotionalStability + Openness, data = lab7)
tab_model(model_lab7, show.std = TRUE)
plot_model(model_lab7,  type ="std",  show.values = TRUE, vline.color = "#1B191999", line.size = 1.5, dot.size = 2.5, colors = "blue") + theme_bruce()

```

# Q3: Interpret the R2. Which personality trait(s) can explain unique variance in satisfaction with life when controlling for each other, and which ones cannot? If someone asks you for advice on how to improve life satisfaction, based on your results, which personality trait would you recommend them to change and why? 

13.8% variance in the satifaction with life can be explained by the variance in Extraversion, Agreeableness, Conscientiousness, EmotionalStability, and Openness.
Extraversion, EmotionalStability, and Openness can explain unique variance in satisfaction with life when controlling for each other, and Agreeableness and Conscientiousness cannot.
Advice: Increasing Extraverted behaviors, such as engaging more in social activities, building relationships, and becoming more outgoing, could lead to higher life satisfaction.
Improving Emotional Stability (or reducing Neuroticism) by managing stress, reducing anxiety, and developing coping mechanisms for emotional regulation would likely enhance life satisfaction as well. Should not be extremely open to this world, or your satisfaction with life will drop.